HW 3_Bryan

### 2020-10-07 HW3/HW 3_Bryan.Rmd
Update HW 3_Bryan.Rmd
Adding more exploring plots

```{r}
library(tidyverse)
library(kableExtra)
library(corrplot)
```

@@

>>>>

```{r}
library(tidyverse)
library(kableExtra)
library(corrplot)
library(ggplot2)
library(GGally)
```

@@

```{r}
corrplot(correlation, type = "lower", order="hclust", tl.col = "black", tl.srt = 45, method = "number")

```

```{r, fig.width=14, fig.height=12}
ggpairs(as.data.frame(correlation), lower = list(continuous = "points", combo = "facethist", discrete = "facetbar", na =
    "na"))

```
